---
title: "Solving knapsack problem from different approaches"
author: "Teno González Dos Santos, Jose Luis López Ruiz, Enrique Josué Álvarez Robles"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette documents the content provided in the package knapsack 1.0.0. This is a high-level adjunct to the low-level details found in *?brute_froce_knapsack*, *?greedy_knapsack* and *?knapsack_dynamic*. You’ll learn how to work with *knapsack* package by using the previous methods which will allow you to solve the knapsack problem from different approaches.

```{r, include = FALSE}
library(devtools)
devtools::install_github("pepelu8000/ARP_Lab6", subdir="knapsack")
library(knapsack)
```


## Using package *knapsack*
This package comes with a set of useful functions that allows you to solve the knapsack problem for a set of objects and a specific capacity from different approaches.

### creating your fixed set of objects
For our examples we are using a fixed set of objects with their values and weights. This allows you to compare different approaches for the same input.

```{r creating_set}
set.seed(42)
n <- 1000000
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE), v=runif(n = n, 0, 10000))
```

### brute_force_knapsack()
This function goes through all possible alternatives and returns the maximum value found. This approach is of complexity O(2^n) since all possible combinations 2^n needs to be evaluated. It is used in the following way:

```{r brute_force_knapsack}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```

**Question. How long time does it takes to run the algorithm for n = 16 objects?**

```{r brute_force_knapsack_t}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
```

### knapsack_dynamic()
This function uses the following approach: if the weights are actually discrete value we can use this to create an algorithm that can solve the knapsack problem exact by iterating over all possible values of w. It is used in the following way:

```{r knapsack_dynamic}
knapsack_dynamic(x = knapsack_objects[1:40,], W = 3500)
```

**Question. How long time does it takes to run the algorithm for n = 500 objects?**

```{r knapsack_dynamic_t}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```

### greedy_knapsack()
This function sorts the items in decreasing order of value per unit of weight, *v_i/w_i*. It then proceeds to insert them into the sack, starting with as many copies as possible of the first kind of item until there is no longer space in the sack for more. Provided that there is an unlimited supply of each kind of item, if *m* m is the maximum value of items that fit into the sack, then the greedy algorithm is guaranteed to achieve at least a value of *m/2*. It is used in the following way:

```{r greedy_knapsack}
greedy_knapsack(x = knapsack_objects[1:100,], W = 3500)
```

**Question. How long time does it takes to run the algorithm for n = 1000000 objects?**

```{r greedy_knapsack_t}
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500))
```